---
title: "delete soon"
output: html_document
date: "2025-09-28"
editor_options: 
  chunk_output_type: console
---

#### First, of course, you do the three basic libraries
```{r message=FALSE, warning=FALSE}
library(data.table)
library(tidyverse)
library(ggplot2)

```

# DOLLAR SIGN NOTATION 
Then, we learned that by sandwiching text in between dollar signs, you are able to create fancy, italicized letters. 

#### $a+b = c$ makes the line below: 
$a+b =c$ 

$\text{a}+b$

# Here, you do some basic commands for arithmetic

## ADD

a+b=c
```{r}
10+2
```

## MULTIPLY 

a*b=c
```{r}
10*2
```

## SUBTRACT 

a-b=c
```{r}
10-2
```


# PLOTTING 

### In order to show some basic graphs (histogram, density plot, bar graph, and a scatter plot) you do some setup and then use essentially the same line with slight changes. 
```{r}
df <- fread ("https://colauttilab.github.io/RCrashCourse/FallopiaData.csv")
head(df)
glimpse(df)
df$Scenario <- as.factor(df$Scenario)
```

#### So since the setup commands are done, let's now do the commands to plot them on different graphs: 

```{r}


ggplot(aes(x=Total), data=df) + geom_histogram()

ggplot(aes(x=Total), data=df) + geom_density()

ggplot(aes(x=Scenario), data=df) + geom_bar()

ggplot(aes(x=Silene, y=Total), data=df) + geom_point()

```

#### The last two types of graphs are both dotplots, but they're slightly different. 

The first way is using dotplots for individual variables 
```{r}
ggplot(aes(x=Total), data=df) +
  geom_dotplot(binwidth=2)
```

The second way is to use dotplots for continuous by categorical data. This time, we piped df to the rest of the text by doing a pipe operator at the beginning of the data instead of adding it into the parentheses like you did before
```{r}

df %>% ggplot(aes(x=Nutrients, y=Total)) +
  geom_dotplot(binaxis="y", binwidth=2)

```

Also, doing git add . into the terminal is called staging. You do it to put everything into the staging area. You do that before you commit if you've made changes since your last commit. 